Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-29 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

L3$label <- "Value"
i = 1
for (i in 1:nrow(L3)) {
  if (L3$model[i] == "q3_pp_u_1") {
    sett -> L3$q3_setting_1[i]
  }else{
    sett -> L3$q3_setting_2[i]
  }
  L3$label[i] <- paste(L3$author_1[i], " [", sett, "]", sep = "")
}

>>>>

L3$label <- "Value"
i = 1
for (i in 1:nrow(L3)) {
  if (L3$model[i] == "q3_pp_u_1") {
    L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_1[i], "]", sep = "")
  }else{
    L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_2[i], "]", sep = "")
  }
